\section{Takeaways}

This work formalizes the previously imprecise notion of constant-time programming, in addition to providing a publicly available and fully automated tool that can verify (in seconds) whether implementations of cryptographic algorithms from off-the-shelf libraries adhere to the notion of constant-time.
This is, undoubtedly, an impressive result.

That said, the paper does have a few weaknesses: \\
\indent Firstly, \ctVerif requires LLVM implementations which is problematic for two reasons.
Cryptographic code is often written directly in assembly due to the performance benefits. For instance, Vale~\cite{vale} demonstrates that OpenSSL assembly implementations outperform their C counterparts by up to 50\%.
Further, verifying that LLVM code runs in constant time does not guarantee that the executable runs in constant time~\cite{KaufmannPVV16}. To the authors' credit, they do discuss such scenarios.

Secondly, the formalization of constant-time as presented by the papers is significantly weakened by the advent of micro-architectural attacks (~\cite{meltdown, spectre}). To be fair to the authors, such attacks became popular after their paper was published. Further, one could argue that such attacks are not a property of the implementation, and are a menace that the underlying hardware/operating system must tackle.

Finally, the authors do not present a single example where their ``automated'' approach fails to verify constant-timeliness in reasonable time. As such, the results look a little too good to be true.

During the course of this project, we plan to investigate the first and third aspects of \ctVerif more thoroughly.
Specifically, we aim to identify where the tool falls short and also patch it with LLVM-passes that can preserve constant timeliness.
